Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-08-29 public/paper/pyg4ometry.tex
Updated complete model figure

An example of the VTK output for code listing XXX is shown in Figure~\ref{fig:rapidModellingExample}.
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
\caption{VTK visualisation output from code example XXX.}
\label{fig:rapidModellingExample}
\end{center}
\end{figure}
Significantly more complex geometries can be developed using a structure similar to that shown in code listing XXX.

\subsection{Discussion}

@@

\begin{lstlisting}[caption={A simple pyg4ometry python script to load a FLUKA file},label={lst:pythonFLUKALoading}, language=Python]
    reader_faraday  = pyg4ometry.fluka.Reader("faradayCup2.inp")
    faraday_greg    = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
    faraday_logical = faraday_greg.getWorldVolume()
    faraday_assembly = faraday_logical.assemblyVolume()
\end{lstlisting}

@@

\begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
    reader_dipole = pyg4ometry.freecad.Reader("./10_SectorBendMedium.step")
    reader_dipole.relabelModel()
    reader_dipole.convertFlat()
    dipole_reg = reader_dipole.getRegistry()
\end{lstlisting}

>>>>

An example of the VTK output for code listing \ref{lst:pythonRapidModelling} is shown in Figure~\ref{fig:rapidModellingExample}.
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
\caption{VTK visualisation output from code listing \ref{lst:pythonRapidModelling}.}
\label{fig:rapidModellingExample}
\end{center}
\end{figure}
Significantly more complex geometries can be developed using a structure similar to that shown in code 
listing \ref{lst:pythonRapidModelling}.

@@

\begin{lstlisting}[caption={A simple pyg4ometry python script to load a FLUKA file},label={lst:pythonFLUKALoading}, language=Python]
    reader      = pyg4ometry.fluka.Reader("faradayCup2.inp")
    g4_reg     = pyg4ometry.convert.fluka2Geant4(reader.flukaregistry)
    logical      = g4_reg.getWorldVolume()
\end{lstlisting}

@@

\begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
    reader = pyg4ometry.freecad.Reader("FileName.step")
    reader.relabelModel()
    reader.convertFlat()
    logical = reader.getRegistry().getWorldVolume()
\end{lstlisting}
